---
title: "Vascular Surgery Exam Prep"
author: "Editors: Adam Johnson, MD, MPH; Matt Smith, MD, PhD; and Audible Bleeding"
date: "DRAFT - `r Sys.Date()`"
output: pdf_document
documentclass: book
bibliography: [references.bib, packages.bib]
csl: apa-numeric-superscript-brackets.csl
url: https://adam-mdmph.github.io/VS-Exam-Prep/
description: |
  This is an ebook version of exam preparation content produced for Audible Bleeding: The Vascular Surgery Podcast, powered by the Society for Vascular Surgery
link-citations: yes
github-repo: https://github.com/adam-mdmph/VS-Exam-Prep
site: bookdown::bookdown_site
apple-touch-icon: "images/apple_icon.png"
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(devtools)

devtools::install_github("mccarthy-m-g/embedr")
library(embedr)
```

# About

This content was developed by the [Audible Bleeding Team](https://www.audiblebleeding.com/about-1/) to accompany our board review podcast series. Each chapter covers a key domain of vascular surgery, essential for board review preparation, and is associated with an Audible Bleeding episode which you can access through the link embeded into the text.

## Usage

This e-book is not intended to be a comprehensive board review guide, but instead serves as an easily accessible resource, paired with our podcast content to help streamline exam preparation.

Please consider this a "living document." We plan to post regular updates and respond to your feedback. We are utilizing an open source annotations software called [hypothes.is](https://web.hypothes.is) to allow you to take note along side our e-book. Feel free to post your notes publically if you think other readers would benefit from your additions, or create a small private group for your local trainees of faculty members. We will work to incorporate relevant notes and additions into future editions.

## Comments, Questions or Contributions

Please visit our [github page](https://github.com/adam-mdmph/VS-Exam-Prep) or [send us an email](mailto:audiblebleeding@vascularsociety.org).

## Authors and Contributors

**Danielle Bajakian, MD;** Assistant Professor of Vascular Surgery; Director, Critical Limb Ischemia Program; *Columbia University, New-York Presbyterian*

**Mohamed Barkat, MSc, FRCS (Vasc);** Consultant Vascular Surgeon; *Manchester University NHS Foundation Trust;* [\@mo_barkat](https://twitter.com/mo_barkat)

Einar Brevik, MD; Consultant Vascular Surgeon; Haukeland University Hospital

**Sarah J. Carlson, MD, MSc, FACS;** Professor of Vascular Surgery, Associate Chief for Surgery Operations; *Boston University, Boston VA Medical Center;* [\@sarahcarlsonmd](https://twitter.com/sarahcarlsonmd?lang=en)

Marlin "Wayne" Causey, MD; Chief of Vascular Surgery; Brooke Army Medical Center.

**Matthew Chia, MD, MS**; Vascular Surgery Resident; *Northwestern*; [\@chia_md](https://twitter.com/chia_md?lang=en)

**Anahita Dua, MD, MS, MBA, FACS;** Assistant Professor of Vascular Surgery; Director of Vascular Laboratory; Co-director of the Peripheral Arterial Disease Center; *Harvard University, Massachusetts General Hospital;* [\@AnahitaDua](https://twitter.com/anahitadua)

Julie Duke, MD, RPVI; Vascular Surgeon; University of Minnesota

Matthew Edwards, MD; Richard H. Dean Professor and Chairman of Vascular and Endovascular Surgery; Atrium Health Wake Forest Baptist; [\@msedwards0427](https://mobile.twitter.com/msedwards0427)

**Sharif Ellozy, MD;** Associate Professor of Vascular Surgery, Vascular Surgery Fellowship Program Director; *Weill Cornell Medical College, New-York Presbyterian;* [\@SharifEllozy](https://twitter.com/sharifellozy)

**Adham Elmously, MD**; Cardiothoracic Surgery Fellow; *Houston Methodist;* [\@elmouslyMD](https://twitter.com/elmouslymd?lang=en)

Leanna Erete, MBBS; Vascular Surgery Trainee; London Deanery; [\@leanna_erete](https://twitter.com/leanna_erete?lang=en)

Alex Forsyth, MD; Vascular Surgery Resident; University of Massachusetts; [\@alex_forsyth\_](https://twitter.com/alex_forsyth_)

**Rachael Forsythe, MBChB, PhD**; Consultant Vascular Surgeon; *Royal Infirmary Edinburgh;* [\@ROForsythe](https://twitter.com/roforsythe?lang=en)

Nick Greaves, MD; Consultant Vascular Surgeon; Manchester Royal Infirmary

Manj Gohel, MBChB, MD, FRCS, FEBVS; Consultant Vascular Surgeon; Nuffield Health; [\@ManjGohel](https://twitter.com/manjgohel)

**Eilidh Gunn, MBChB, MRCSEd;** Clinical Research Fellow, Vascular Surgery; *Royal Infirmary Edinburgh;* [\@eil1_g](https://twitter.com/eil1_g)

Michael Jenkins, BSc, MBBS, MS, FRCS, FEBVS; Consultant Vascular Surgeon; St Mary's Hospital, Imperial College Healthcare NHS Trust and Chelsea and Westminster Hospitals; [\@mpj21165](https://mobile.twitter.com/mpj21165)

**Adam P. Johnson, MD, MPH;** Consultant Vascular Surgeon; *Royal Infirmary Edinburgh;* [\@adam_mdmph](https://twitter.com/adam_mdmph?lang=en)

Nedal Katib, MBBS, MS; Consultant Vascular Surgeon; South Eastern Sydney Local Health District

**MAJ Kevin Kniery, MD, MPH;** Vascular Surgeon; *Brooke Army Medical Center;* [\@Kniery_Bird](https://twitter.com/kniery_bird)

**Young Lee, MD;** Vascular Surgery Fellow; *Emory University;* [\@youngclee86](https://twitter.com/youngclee86)

Joseph Lombardi, MD, MBA; Professor and Chief of Vascular Surgery; Cooper University Hospital; [\@VascSurgMD](https://twitter.com/vascsurgmd)

**Rafael Demarchi Malgor, MD, MBA, FACS;** Associate Professor of Surgery; Program Director, Robert B. Rutherford fellowship and residency in Vascular Surgery; Division of Vascular Surgery and Endovascular Therapy; *The University of Colorado, Anschutz Medical Center;* [\@RafaMalgor](https://twitter.com/rafamalgor)

M. Asharf Mansour, MD; Academic Chair, Vascular Surgeon; Michigan State University, Spectrum Health

**Nicolas J Mouawad, MD, MPH, MBA, FSVS, FRCS, FACS, RPVI;** Chief and Medical Director of Vascular and Endovascular Surgery; *McLaren Health System - Bay Region, Michigan, USA*; Associate Clinical Professor of Surgery, *Michigan State University, Central Michigan University*; [\@NickMouawadMD](https://twitter.com/nickmouawadmd?lang=en)

Cullen McCarthy, MD; Vascular Surgeon; Cardio-Thoracic & Vascular Surgical Associates, Mobile Infirmary

Mia Miller, MD

Andrew Nickinson, MD; Vascular Surgery Trainee; Wessex Deanery; [\@AndrewNickinson](https://twitter.com/andrewnickinson)

Anna Ohlsson, MD; Vascular Surgeon; Corporal Michael J. Crescenz/Philadelphia VA Medical Center

**Alaska Pendleton, MD, MPH;** Vascular Surgery Resident; *Massachusetts General Hospital*

Todd Rassmussen, MD; Professor of Surgery, Vice-Chair of education; Mayo Clinic; [\@trasmussen_md](https://mobile.twitter.com/trasmussen_md)

**Nicole Rich, MD, MPH;** Vascular Surgeon; *Ascension Medical Group Saint Thomas Rutherford Surgery*

Sherene Shalhub, MD; Associate Professor of Surgery, Division of Vascular Surgery; University of Washington; [\@shereneshalhub](https://twitter.com/shereneshalhub)

Kush Sharma, MD; Vascular Surgeon; Desert Vein & Vascular Institute

**Sammy Siada, DO, RPVI;** Assistant Clinical Professor of Vascular and Endovascular Surgery; *UCSF Fresno;* [\@SammySiada](https://twitter.com/sammysiada)

Aminder Singh, MD; Vascular Surgery Trainee, NIHR Academic Clinical Fellow in Vascular Surgery; University of Cambridge, East of England; [\@AminderASingh](https://twitter.com/aminderasingh)

**Matthew R. Smeds, MD, FACS, DFSVS;** Professor of Surgery, Division of Vascular and Endovascular Surgery; *St Louis University*; [\@mattsmeds](https://twitter.com/mattsmeds?lang=en)

**Matthew Smith, MD, PhD;** Assistant Professor of Surgery, Division of Vascular Surgery; *University of Washington*

Matt Spreadbury, MD; Vascular Surgery Resident; Haukeland University Hospital

```{r include=FALSE}
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'embedr'
), 'packages.bib')
```
