---
title: "Vascular Surgery Exam Prep"
author: "Editors: Adam Johnson, MD, MPH; Matt Smith, MD, PhD; and Audible Bleeding"
date: "DRAFT - `r Sys.Date()`"
output: pdf_document
documentclass: book
bibliography: [references.bib, packages.bib]
csl: apa-numeric-superscript-brackets.csl
url: https://adam-mdmph.github.io/VS-Exam-Prep/
description: |
  This is an ebook version of exam preparation content produced for Audible Bleeding: The Vascular Surgery Podcast, powered by the Society for Vascular Surgery
link-citations: yes
github-repo: https://github.com/adam-mdmph/VS-Exam-Prep
site: bookdown::bookdown_site
apple-touch-icon: "images/apple_icon.png"
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(devtools)

devtools::install_github("mccarthy-m-g/embedr")
library(embedr)
```

# About

This content was developed by the [Audible Bleeding Team](https://www.audiblebleeding.com/about-1/) to accompany our board review podcast series. Each chapter covers a key domain of vascular surgery, essential for board review preparation, and is associated with an Audible Bleeding episode which you can access through the link embeded into the text.

## Usage

This e-book is not intended to be a comprehensive board review guide, but instead serves as an easily accessible resource, paired with our podcast content to help streamline exam preparation.

Please consider this a "living document." We plan to post regular updates and respond to your feedback. We are utilizing an open source annotations software called [hypothes.is](https://web.hypothes.is) to allow you to take note along side our e-book. Feel free to post your notes publically if you think other readers would benefit from your additions, or create a small private group for your local trainees of faculty members. We will work to incorporate relevant notes and additions into future editions.

## Comments, Questions or Contributions

Please visit our [github page](https://github.com/adam-mdmph/VS-Exam-Prep) or [send us an email](mailto:audiblebleeding@vascularsociety.org).

## Authors and Contributors

### Authors

**Mohamed Barkat**; Consultant Vascular Surgeon; *Manchester University NHS Foundation Trust*

**Einar Brevik**; Consultant Vascular Surgeon; *Haukeland University Hospital*

**Matthew Chia, MD**; Vascular Surgery Resident; Northwestern

**Anahita Dua, MD**; Assistant Professor of Vascular Surgery; Director of Vascular Laboratory; Co-director of the Peripheral Arterial Disease Center; *Harvard University, Massachusetts General Hospital.*

Julie Duke

Matthew Edwards

**Adham Elmously, MD**; Cardiothoracic Fellow; *Houston Methodist*

Alex Forsyth

**Rachael Forsythe, MBBS**; Consultant Vascular Surgeon; *Royal Infirmary Edinburgh*

Nick Grieves

Manj Gohel

Michael Jenkins

Adam P. Johnson, MD, MPH

Nedal Katib

Kevin Kneiry, MD, MPH

Young Lee, MD

**Joseph Lombardi, MD;** Professor and Chief of Vascular Surgery; *Cooper University Hospital* 

**Rafael Demarchi Malgor, MD, MBA, FACS;** Associate Professor of Surgery; Program Director, Robert B. Rutherford fellowship and residency in Vascular Surgery; Division of Vascular Surgery and Endovascular Therapy; *The University of Colorado, Anschutz Medical Center*

Asharf Mansour, MD

Nick Mouawad

Cullen McCarthy

Mia Miller

Andrew Nickinson

Anna Ohlsson

**Alaska Pendleton, MD**; Vascular Surgery Resident; *Massachusetts General Hospital*

Todd Rassmussen, MD

Nicole Rich, MD, MPH

Sherene Shalhub, MD

Kush Sharma, MD

**Sammy Siada, DO, RPVI;** HS Assistant Clinical Professor; Vascular and Endovascular Surgery; *UC Fresno*

Aminder Singh

Matt Smeds, MD

**Matt Spreadbury, MD**; Vascular Surgery Resident; *Haukeland University Hospital*

### Contributors

Sharif Ellozy

Eilidh Gunn

Leanna Erete

```{r include=FALSE}
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'embedr'
), 'packages.bib')
```
